



    Farmer John has lined up his N (1 ≤ N ≤ 100,000) cows in a row to measure their heights; cow i has height H\_i (1 ≤ H\_i ≤ 1,000,000,000) nanometers--FJ believes in precise measurements! He wants to take a picture of some contiguous subsequence of the cows to submit to a bovine photography contest at the county fair.   

    The fair has a very strange rule about all submitted photos: a photograph is only valid to submit if it depicts a group of cows whose median height is at least a certain threshold X (1 ≤ X ≤ 1,000,000,000).   

    For purposes of this problem, we define the median of an array A[0...K] to be A[ceiling(K/2)] after A is sorted, where ceiling(K/2) gives K/2 rounded  up to the nearest integer (or K/2 itself, it K/2 is an integer to begin with). For example the median of \{7, 3, 2, 6\} is 6, and the median of \{5, 4, 8\} is 5.   

    Please help FJ count the number of different contiguous subsequences of his cows that he could potentially submit to the photography contest.   

\subsubsection{   Input  }
\begin{itemize}
	\item      Line 1: Two space-separated integers: N and X.    
	\item      Lines 2..N+1: Line i+1 contains the single integer H\_i.    
\end{itemize}

\subsubsection{   Output  }
\begin{itemize}
	\item      Line 1: The number of subsequences of FJ's cows that have median at         least X. Note this may not fit into a 32-bit integer.    
\end{itemize}

\subsubsection{   Example  }
\begin{verbatim}
\textbf{Input:}
\\4 6 
\\10 
\\5 
\\6 
\\2 
\\
\\\textbf{Output:}
\\7 
\\
\\\end{verbatim}

\textbf{     Explain:    }    There are 10 possible contiguous subsequences to consider. Of these, only 7 have median at least 6. They are \{10\}, \{6\}, \{10, 5\}, \{5, 6\}, \{6, 2\}, \{10, 5, 6\}, \{10, 5, 6, 2\}.   