

 The definition of beauty quotes sequence:Empty string is a series of beautiful quotes.If X is a series of beautiful quotes, then [X], (X), \{X\} is also a beautiful array brackets.If X, Y ranges are 2 beautiful quotation marks, the sequence XY is also beautiful.Example: () [() ()] is a row of beautiful quotes. \{[)\} Is not beautiful array brackets.Given a string S contains only the brackets. When writing out the characters from position to position i of the string S j (1 $<$= i $<$= j $<$= Length (S)) we obtain the sequence S (i, j). An S (i, j) is the better of the string S if S (i, j) is a series of beautiful quotes. Request the number of good properties of S.

The definition of beauty quotes sequence:

Empty string is a series of beautiful quotes.

If X is a series of beautiful quotes, then [X], (X), \{X\} is also a beautiful array brackets.

If X, Y ranges are 2 beautiful quotation marks, the sequence XY is also beautiful.

Example: () [() ()] is a row of beautiful quotes. \{[)\} Is not beautiful array brackets.

Given a string S contains only the brackets. When writing out the characters from position to position i of the string S j (1 $<$= i $<$= j $<$= Length (S)) we obtain the sequence S (i, j). An S (i, j) is good substring of string S if S (i, j) is a series of beautiful quotes. Request the number of good substring of S.

\subsubsection{Input}

A single line: string S.

The first 10 trials, the length of S is less than 101.

The next 10 trials, the length of S is less than 10001.

10 final test, the length of S is less than 1000001.

\subsubsection{Output}

A single integer: Number of possible substring of S.

\subsubsection{Example}
\begin{verbatim}
\textbf{Input:}
(){](({}))[]

\textbf{Output:}
6\end{verbatim}