

 For the S matrix has n rows and m columns. Initially, all elements are equal to 1. Have a query Q in two forms:1 xy Val: Raising element S [x, y] to Val units.2 xyuv M: Let the numbers in the matrix of the cell is left on the x, y and bottom right box is u, v in module M.As a young man serious, plus code such as wind speed, AC thai9cdb quickly and receive the entire award (delicious "\textasciicircum \textasciicircum). However, the other members of the team as Tuan Anh, South Cay, Vietnam proved quite embarrassing cats and they need your help.InputLine 1 contains three numbers: n, m, Q.Q lines follow, each containing a query in one of two forms above.outputFor each query type 2, in the results as required.ExampleInput:2 3 32 1 1 1 3 21 2 2 22 1 2 2 3 3output:10limit10 first test with n, m $<$101. Q $<$10001.The next test is 10 n, m $<$1001. Q $<$101.The next test is 10 n, m $<$1001. Q $<$50001.At all time points, 0 $<$| S [i, j] | $<$1001.Base $<$100 000 008.

For the S matrix has n rows and m columns. Initially, all elements are equal to 1. Have a query Q in two forms:

 

1 x y Val: Raising element S [x, y] to Val units.

 

2 x y u v Base: Let the numbers

R(x,y,u,v)=(S[x,y]*S[x,y+1]*...*S[x,v])*(S[x+1,y]*S[x+1,y+1]*...*S[x+1,v])*...*(S[u,y]*S[u,y+1]*...*S[u,v]) module Base.

 

Input

 

Line 1 contains three numbers: n, m, Q.

 

Q lines follow, each containing a query in one of two forms above.

 

output

 

For each query type 2, in the results as required.

 

Example

 

Input:

2 3 3

2 1 1 1 3 2

1 2 2 2

2 1 2 2 3 3

 

output:

1

0

 

Note:

10 first test with n, m $<$101. Q $<$10001.

10 test next with n, m $<$1001. Q $<$101.

10 final test with n, m $<$1001. Q $<$50001.

At all time, 0 $<$| S [i, j] | $<$1001.

Base $<$100 000 008.

 